---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# palint  
  
The goal of `palint` is to have a package with helper functions to calculate palaeoclimate interactions. It is currently used privately but the goal is to add all functions I have used in the past in here. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Ischi94/palint")
```
## Example  
  
The package currently contains one function: `perc_change`. It calculates the percentage change between two values: 

```{r perc_change example1}
library(palint)
perc_change(2, 4)
```  
  
The default returns the raw value, but by changing the `print.result` parameter we can get the raw value expressed as percentage or in a text description:  
  
```{r perc_change example2}
perc_change(2, 4, "percentage")
``` 

```{r perc_change example3}
perc_change(2, 4, "text")
``` 



